Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-30 latex/afm-cs-main.tex
tweak abstract.
Update on Overleaf.

\author{Roger A. Braker, \textit{Student Member, IEEE}, Yufan Luo, \textit{Student Member, IEEE} , Lucy Y. Pao, \textit{Fellow, IEEE} and Sean B. Andersson, \textit{Senior Member, IEEE, and Member, ASME}
  \thanks{Braker and Pao are with the Dept. of Electrical, Computer, and
    Energy Engineering at the University of Colorado, 425 UCB,
    Boulder, CO 80309, USA. %Phone: +1 (303) 492-2360. Fax:
    +1 (303) 492-2758.}%R. A. Braker (corresponding author
    %roger.braker@colorado.edu) is a graduate student and L.Y. Pao
    %(pao@colorado.edu) is the Palmer  Professor.}
    \thanks{Luo is with the Division of Systems Engineering and Andersson is with the Division of Systems Engineering and the Department of Mechanical Engineering, Boston University, Boston, MA 02215, USA.}
  \thanks{This work was supported in part by the US National Science
    Foundation (NSF Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729)  Agilent Technologies,
    Inc., and the Hanse-Wissenschaftskolleg Institute for Advanced Study in Delmenhorst, Germany.} }

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim
  to reduce the time to acquire an image by reducing the number of
  measurements needed while still maintaining image quality. The approach consists of two components: data acquisition and image reconstruction. While the underlying idea is straightforward, practical implementation of a working scheme involves solving a variety of non-trivial problems. In this
  paper, we describe one such hardware implementation and demonstration based on the use of collections of short scans
  known as $\mu$--paths. Using a commercial AFM, we acquire data on a
  grating sample. Reconstructions are made from these data using
  a new variant of basis pursuit, Basis Pursuit with Vertical
  Variation, that is designed to reduce artifacts arising from
  the sampling pattern. The quality of the resulting images is
  compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio
  and the structured similarity index metric and a new metric we call
  the relative damage index. These images are compared (across a range of scan speeds)
  to both standard raster
  scans as well as to simple subline sampling where only a subset of the
  rows of the image are acquired (followed by reconstruction).
  These experiments show that at low sampling densities and slow scan rates,
  $\mu$-path scanning achieves better image quality in less time than subline sampling.
  Conversely, for faster scan rates and higher densities, subline sampling
  achieves better image quality in less time.
  % These experiments demonstrate that at slow scan
  % rates, the $\mu-$path scheme produces similar image quality with
  % significantly less sampling (and thus less tip-sample interaction)
  % and that at high rates, the undersampling scheme produces higher
  % quality images than raster scanning.
\end{abstract}

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the AFM control loop for all three axes.
    Not shown is anti-windup for the $Z$-axis integrator, which is active
    when $r_Z=\rzup$ (states 1 and 5) where sensor saturation is possible.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
After the tip-descent, we begin scanning in a ``pre-scan'' phase
(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
have observed that there is less noise in the deflection signal while
the $XY$-stage is in motion compared to sitting still. Second, and more
importantly, it lets us bring the $X$-axis to its scanning velocity at
the same time the transients from the $Z$-axis die out. Without this,
we must extend the $\mu$-path by a distance equal to the steady-state
error following a ramp. For an arbitrary scan speed, this means the
$\mu$-path scan would need an extra
\begin{equation}
  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_X}{z-1}\right\rceil
\end{equation}
time steps, where $H_X$ is closed-loop transfer function for the
$X$-axis. For our system $N=111$. By initiating the scan while the
$Z$-axis settles, we eliminate much of this overhead.

>>>>

\author{Roger A. Braker, \textit{Student Member, IEEE}, Yufan Luo, \textit{Student Member, IEEE} , Lucy Y. Pao, \textit{Fellow, IEEE} and Sean B. Andersson, \textit{Senior Member, IEEE, and Member, ASME}
  \thanks{Braker and Pao are with the Dept. of Electrical, Computer, and
    Energy Engineering at the University of Colorado, 425 UCB,
    Boulder, CO 80309 USA. %Phone: 
    +1 (303) 492-2360.} 
    %Fax:
    %+1 (303) 492-2758.}%R. A. Braker (corresponding author
    %roger.braker@colorado.edu) is a graduate student and L.Y. Pao
    %(pao@colorado.edu) is the Palmer  Professor.}
    \thanks{Luo and Andersson are with the Division of Systems Engineering and Andersson is also with the Department of Mechanical Engineering, Boston University, Boston, MA 02215 USA.}
  \thanks{This work was supported in part by the US National Science
    Foundation (NSF Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729), Agilent Technologies,
    Inc., a Palmer Endowed Chair Professorship, and the Hanse-Wissenschaftskolleg Institute for Advanced Study in Delmenhorst, Germany.} }

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim
  to reduce the time to acquire an image by reducing the number of
  measurements needed while still maintaining image quality. The approach consists of two components: data acquisition and image reconstruction. While the underlying idea is straightforward, practical implementation of a working scheme involves solving a variety of non-trivial problems. In this
  paper, we describe one such hardware implementation and demonstration based on the use of collections of short scans
  known as $\mu$--paths. Using a commercial AFM, we acquire data on a
  grating sample. Reconstructions are made from these data using
  a new variant of basis pursuit, Basis Pursuit with Vertical
  Variation, that is designed to reduce artifacts arising from
  the sampling pattern. The quality of the resulting images is
  compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio
  and the structured similarity index metric and a new metric we call
  the relative damage index. These images are compared (across a range of scan speeds)
  to both standard raster
  scans as well as to simple subline sampling where only a subset of the
  rows of the image are acquired (followed by reconstruction).
  These experiments show that at low sampling densities and slow scan rates,
  $\mu$-path scanning achieves better image quality in less time than subline sampling.
  Conversely, for faster scan rates subline sampling is faster and, for higher sampling
  densities, achieves comparable image quality.
  % These experiments demonstrate that at slow scan
  % rates, the $\mu-$path scheme produces similar image quality with
  % significantly less sampling (and thus less tip-sample interaction)
  % and that at high rates, the undersampling scheme produces higher
  % quality images than raster scanning.
\end{abstract}

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the AFM control loop for all three axes.
    Not shown is anti-windup for the $Z$-axis integrator, which is active
    when $r_Z=\rzup$ (states (1) and (5)) where sensor saturation is possible.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
After the tip-descent, we begin scanning in a ``pre-scan'' phase
(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
have observed that there is less noise in the deflection signal while
the $XY$-stage is in motion compared to sitting still. Second, and more
importantly, it lets us bring the $X$-axis to its scanning velocity at
the same time the transients from the $Z$-axis die out. Without this,
we must extend the $\mu$-path by a distance equal to the steady-state
error following a ramp. For an arbitrary scan speed, this means the
$\mu$-path scan would need an extra
\begin{equation}
  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_X}{z-1}\right\rceil
\end{equation}
time steps, where $H_X$ is closed-loop transfer function for the
$X$-axis. For our system $N=111$. By initiating the scan while the
$Z$-axis settles, we eliminate much of this overhead.

### 2019-06-30 latex/coverletter.tex
Update on Overleaf.

It is our pleasure to submit this manuscript entitled \textit{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction} (authored by Roger A. Braker, Yufan Luo, Lucy Y. Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics. This paper is submitted for possible publication in the Focused Section on Nano/Micro Motion  Systems:  Design,  Sensing  and  Control(NMMS).

@@

The manuscript has not been published nor is it under review elsewhere. All four authors agree to submit the manuscript in its present form to the IEEE/ASME Transactions Mechatronics focused section NMMS. This work was supported in part by Agilent Technologies, Inc, The US National Science Foundation (under Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729), and the Hanse Wissenschaftskolleg in Delmenhorst, Germany. Thank you for the consideration and we look forward to hearing from you.

>>>>

It is our pleasure to submit this manuscript entitled \textit{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction} (authored by Roger A. Braker, Yufan Luo, Lucy Y. Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics. This paper is submitted for possible publication in the Focused Section on Nano/Micro Motion  Systems:  Design,  Sensing  and  Control (NMMS).

@@

The manuscript has not been published nor is it under review elsewhere. All four authors agree to submit the manuscript in its present form to the IEEE/ASME Transactions on Mechatronics focused section on NMMS. This work was supported in part by Agilent Technologies, Inc., the US National Science Foundation (under Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729),
a Palmer Endowed Chair Professorship,
and the Hanse Wissenschaftskolleg in Delmenhorst, Germany. Thank you for the consideration and we look forward to hearing from you.
